---
title: "Homework R batch 10"
author: "p"
date: "2024-07-20"
output: html_document
---

## This is a homework for showing off my skill in visualising data into an information.

### First, let's import the tidyverse library and diamonds data.

```{r}
library(tidyverse)
print("Loaded library for data tinyverse")
```

## Prepare Data
```{r}
small_df <- diamonds %>% 
  sample_n(1000)
```
## View data columns
```{r}
(small_df %>%
   head(10))
```
## My First Chart Homework create 5 chart
```{r}

ggplot(small_df, aes(x = color)) +
  geom_bar(fill = "salmon") +
  geom_text(stat='count', aes(label=after_stat(count)), vjust=-0.5) +
  labs(title = "The number of diamonds for each color",
       caption = "Source: ggplot2 package",
       x = "Color",
       y = "Count")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```
###Price Distribution
```{r}
ggplot() +
  theme_minimal() +
  geom_histogram(data = small_df, mapping = aes(price),bins = 40, fill = "red", col = "black") +
labs(title = "Price Distribution",
       caption = "Source: ggplot2 package",
       x = "Price",
       y = "Count")

```
## Price vs Carat
---
```{r}
ggplot() +
  theme_minimal() +
  geom_point(data = small_df, mapping = aes(carat, price, col = color)) +
  facet_wrap(~ color, ncol = 4) + 
  labs(title = "Price vs Carat", subtitle = "color sub-plot")
```
## Color vs Price:
---
```{r}
ggplot(small_df, aes(x = color, y = price)) +
  geom_boxplot(fill = "gold", color = "black", alpha = 0.2, notch = TRUE, outlier.fill = "red", outlier.color = "red", outlier.size = 3) + 
  theme_minimal() +
  facet_wrap(~ color)
```
Based on this graph, All of color has almost the same median lower than 5000

## Cut Quality vs Price:
---
```{r}
ggplot(small_df, aes(x = cut, y = price)) + 
  geom_boxplot(fill = "gold" , color = "black" , alpha = 0.2, notch = TRUE, outlier.fill = "red", outlier.color = "red", outlier.size = 3)
```

## Mean Price per Carat
```{r}
ggplot(data = small_df, aes(x = carat, y = price)) +
  geom_bar(fill = "salmon",na.rm = TRUE,width = 0.05,stat = "summary", fun = "mean",  position = "dodge")
```

### Proportion

```{r}


```

```{r}
ggplot(small_df, aes(x = "", fill =cut)) +
  geom_bar(width = 1, stat = "count") +
  coord_polar("y", start = 0) + 
  theme_minimal() + 
  geom_text(aes(label = after_stat(count), ),stat = "count", position = position_stack(vjust = 0.5)) +
  labs(title = "Distribution of Diamond Cuts")
              

```
